A Partitioning Algorithm for Maximum Common (Connected) Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-07 paper/paper.tex
Put in partial 33ve results for now
Plain connected plots

\paragraph{No labels, undirected, connected} have yet to be run.

@@

>>>>

\paragraph{Vertex and edge labels, not directed} are in \cref{figure:33ve-cumulative}, and are not in other papers so we should omit this unless we see something interesting.

\paragraph{No labels, undirected, connected} are in \cref{figure:plain-connected-cumulative}.

@@

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ve-cumulative.pdf}
    \caption{MCS 33\% vertex and edge labelled undirected instances, cumulative runtimes}\label{figure:33ve-cumulative}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-plain-connected-cumulative.pdf}
    \caption{Unlabelled undirected instances, connected, cumulative runtimes}\label{figure:plain-connected-cumulative}
\end{figure}
